Report on Certificate Tools

### 2016-09-06 TEX/draft.tex
Finalised a keytool part

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|}
\hline
                        & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
\multirow{-2}{*}{Tools} & Type   & View and information        & License \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
Keygen                  & JKS    &                             &         \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

      \paragraph{Certificate Signing Request}
To generate a Certificate Signing Request generation of a key pair with alias is needed:
\begin{verbatim}
keytool -genkey -alias namealias -keyalg [RSA|DSA] \
        -keysize [length] -keystore [keystore_path | new_keystore_name]
\end{verbatim}
To create a CSR you then need to do:
\begin{verbatim}
keytool -certreq -keyalg [keyalg_from_genkey] -alias [alias_from_genkey] -file certreq.csr -keystore [jks_from_genkey]
\end{verbatim}
Where you need to set -keyalg -alias and -keystore as chosen when generating key pair earlier.

@@

      \paragraph{Specify Type}
With keytool alone it is not possible to make CA certificate.

      \paragraph{Specify path length}
Specifying of path length is not availiable.

@@

    \subsubsection{Certificate Signing Request signing}
Keytool cannot be used to sign Certificate Signing Request.
    \subsubsection{Create combination of private key and signed chain}

    \subsubsection{Specify certificate validity}
Specification of certificate validity is set when generating key pair in \verb+-validity [time]+ option.

@@

    \subsubsection{Support for Cryptographic Service Provider}
%unsure about that but http://stackoverflow.com/questions/6866447/keytool-error-java-security-keystoreexception-bks-not-found

@@

>>>>

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|}
\hline
                        & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
\multirow{-2}{*}{Tools} & Type   & View and information        & License \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
Keygen                  & JKS    & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

      \paragraph{Certificate Signing Request}
To generate a Certificate Signing Request generation of a key pair with alias is needed:
\begin{verbatim}
keytool -genkey -alias namealias -keyalg [RSA|DSA] \
        -keysize [length] -keystore [keystore_path | new_keystore_name]
\end{verbatim}
To create a CSR you then need to do:
\begin{verbatim}
keytool -certreq -keyalg [keyalg_from_genkey] -alias [alias_from_genkey] \
        -file certreq.csr -keystore [jks_from_genkey]
\end{verbatim}
Where you need to set -keyalg -alias and -keystore as chosen when generating key pair earlier.

@@

      \paragraph{Specify Type}
With keytool you can make a self-signed CA certificate by using \verb+-ext ca:true+ option.

      \paragraph{Specify path length}
Specifying of path length is possible while making a certificate by using  \\
\verb+-ext pathlen:[int path length]+ option.

@@

    \subsubsection{Certificate Signing Request signing}
Keytool cannot be used to sign Certificate Signing Request. It can import certificate signed by CA but as a standalone tool cannot sign a CSR with a CA cert.
%I'm sorry but i haven't found a way to sign a CSR with CA cert with keytool alone

    \subsubsection{Create combination of private key and signed chain}
You can import a key pair into a Java KeyStore file along with signed chain if the signed chain is provided and a CA certificate is imported into said Java Keystore.
    \subsubsection{Specify certificate validity}
Specification of certificate validity is set when generating key pair in \verb+-validity [time]+ option.

@@

    \subsubsection{Support for Cryptographic Service Provider}
Support for Cryptographic service provider is native but there is need for a definition of path where the CSR is located.
\begin{verbatim}
-storetype [keystore_type_of_implementation]
-provider [provider_implementation_name]
-providerpath [provider_implementation_type]
\end{verbatim}
%unsure about that but http://stackoverflow.com/questions/6866447/keytool-error-java-security-keystoreexception-bks-not-found

@@

  \subsection{Importing certificates and keys into storage files}
To import certificate use:
\begin{verbatim}
keytool -import -alias [certificate_chosen_alias] \
        -file [certificate_file.ext] -keystore [target_keystore]  
\end{verbatim}

Importing of keys alone is not supported, you need to fold them into a Java KeyStore or PKCS\#12 file first.
